SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-09-08 scipy-1.0/paper.tex
Uncommented descriptions of each Fortran library

Fortran, despite its age, is still a high-performance scientific programming language with
continued contemporary usage\cite{Koelbel:1993:HPF:562354}. Thus, we wrap the following excellent, field-tested Fortran
libraries in order to provide Python convenience while benefiting from their performance:
FFTPACK\cite{SWARZTRAUBER198445, SWARZTRAUBER198251}, % for performing Fourier transforms,
ODEPACK\cite{hindmarsh1983odepack}, % for solving ordinary differential equation initial value problems,
QUADPACK\cite{piessens1983quadpack}, % for numerical integration of one-dimensional functions,
FITPACK\cite{Dierckx:1993:CSF:151103}, % for curve-fitting and interpolation,
ODRPACK\cite{ODRPACK_Boggs}, % for orthogonal distance regression,
MINPACK\cite{osti_6997568}, % for minimization of linear and nonlinear equations,
ARPACK\cite{leh:sor:yan96}, % for solving large scale eigenvalue problems,
ALGORITHM 644\cite{Amos:1986:APP:7921.214331}, and % for Bessel Functions, and
CDFLIB\cite{CDFLIB_site}. % for evaluation of cumulative density functions.

>>>>

Fortran, despite its age, is still a high-performance scientific programming language with
continued contemporary usage\cite{Koelbel:1993:HPF:562354}. Thus, we wrap the following excellent, field-tested Fortran
libraries in order to provide Python convenience while benefiting from their performance:
FFTPACK\cite{SWARZTRAUBER198445, SWARZTRAUBER198251} for performing Fourier transforms,
ODEPACK\cite{hindmarsh1983odepack} for solving ordinary differential equation initial value problems,
QUADPACK\cite{piessens1983quadpack} for numerical integration of one-dimensional functions,
FITPACK\cite{Dierckx:1993:CSF:151103} for curve-fitting and interpolation,
ODRPACK\cite{ODRPACK_Boggs} for orthogonal distance regression,
MINPACK\cite{osti_6997568} for minimization of linear and nonlinear equations,
ARPACK\cite{leh:sor:yan96} for solving large scale eigenvalue problems,
ALGORITHM 644\cite{Amos:1986:APP:7921.214331} for Bessel Functions, and
CDFLIB\cite{CDFLIB_site} for evaluation of cumulative density functions.
